Waiting time analysis

### 2025-05-19 notebooks/02_waiting_time.qmd
fig: add_labels

```{julia}
using Juno
using Dates
using Discontinuity
using Discontinuity: waiting_time, remove_duplicates
using Discontinuity: plot_wt_pdf, plot_wt_pdf!
using CairoMakie
using Beforerr: easy_save
using AlgebraOfGraphics
using Distributions, DataFramesMeta
using Unitful
using DimensionalData

@@

    g2 = draw!(f[1, 2], data(jtdf) * mapping(M.r, M.ρ_norm))
    ax2 = g2[1].axis
    rfit = curve_fit(model, jtdf.r_mean, jtdf.ρ_norm, [1.0, 1.0])
    lines!(ax2, sort(jtdf.r_mean), model(sort(jtdf.r_mean), rfit.param); color=:gray, linestyle=:dash)
    text!(ax2, (3, 0.8); text=label_model(rfit.param))
    ylims!(ax2, 0.15, 1.05)
    easy_save("fig_occurence_rate")
end
```

>>>>

```{julia}
using Juno
using Dates
using Discontinuity
using Discontinuity: waiting_time, remove_duplicates
using Discontinuity: plot_wt_pdf, plot_wt_pdf!
using CairoMakie
using Beforerr: easy_save, add_labels!
using AlgebraOfGraphics
using Distributions, DataFramesMeta
using Unitful
using DimensionalData

@@

    g2 = draw!(f[1, 2], data(jtdf) * mapping(M.r, M.ρ_norm))
    ax2 = g2[1].axis
    rfit = curve_fit(model, jtdf.r_mean, jtdf.ρ_norm, [1.0, 1.0])
    lines!(ax2, sort(jtdf.r_mean), model(sort(jtdf.r_mean), rfit.param); color=:gray, linestyle=:dash)
    text!(ax2, (3, 0.8); text=label_model(rfit.param))
    ylims!(ax2, 0.15, 1.05)
    add_labels!()
    easy_save("fig_occurence_rate")
end
```
